---
title: "Untitled"
output: github_document
---
---
title: "Deliverable1"
output: github_document
---



## Data Import & Cleaning

```{r problems}
library(tidyverse)
library(tibble)
project <- read_csv("ks-projects-201801.csv")
problems(project) 


```

## Interested variables


```{r variation}
#0-100
group1 <- project %>% filter(usd_goal_real <= 100) %>% select(usd_goal_real)
group1_mean <-sum(group1$usd_goal_real) / 6082
group1_prop <- 6082/378661

#100-1000
group2 <- project %>% filter(usd_goal_real > 100 & usd_goal_real <= 1000) %>% select(usd_goal_real)
group2_mean <- sum(group2$usd_goal_real) / 54811
group2_prop <- 54811/378661

#1000-10000
group3 <- project %>% filter(usd_goal_real > 1000 & usd_goal_real <= 10000) %>% select(usd_goal_real)
group3_mean <- sum(group3$usd_goal_real) / 193351
group3_prop <- 193351/378661

#10000+
group4 <- project %>% filter(usd_goal_real > 10000) %>% select(usd_goal_real)
group4_mean <- sum(group4$usd_goal_real) / 124417
group4_prop <- 124417/378661

usd_goals_data <- data_frame(
  name = c("$0-100", "$101-1000", "$1001-10000", "$10000+"),
  total_avg = c(group1_mean, group2_mean, group3_mean, group4_mean),
  proportion_of_data = c(group1_prop, group2_prop, group3_prop, group4_prop)
)
usd_goals_data



```
In usd_goals_data, we are observing the variability of the goals set by each kickstarter project in US dollars. We see that over 80% of the projects were set to be over 1,000 USD. The majority at 51% was between 1,000 and 10,000 USD. Furthermore, we found the average to see generally within each grouping, what the average was. For example, between 100-1,000 USD, we see that the average was ~$634, which is very near the midway point of the grouping, so this could suggest that there is not much of a certain bracket but more evenly spread out of number of projects that set their goals between 100-1000.

```{r usd_pledged}

#0-100
group1 <- project %>% filter(usd_pledged_real <= 100) %>% select(usd_pledged_real)
group1_pmean <-sum(group1$usd_pledged_real) / 124486
group1_pprop <- 124486/378661

#100-1000
group2 <- project %>% filter(usd_pledged_real > 100 & usd_pledged_real <= 1000) %>% select(usd_pledged_real)
group2_pmean <- sum(group2$usd_pledged_real) / 85108
group2_pprop <- 85108/378661

#1000-10000
group3 <- project %>% filter(usd_pledged_real > 1000 & usd_pledged_real <= 10000) %>% select(usd_pledged_real)
group3_pmean <- sum(group3$usd_pledged_real) / 117758
group3_pprop <- 117758/378661

#10000+
group4 <- project %>% filter(usd_pledged_real > 10000) %>% select(usd_pledged_real)
group4_pmean <- sum(group4$usd_pledged_real) / 51309
group4_pprop <- 51309/378661

usd_pledged_data <- data_frame(
  name = c("$0-100", "$101-1000", "$1001-10000", "$10000+"),
  total_pledged_avg = c(group1_pmean, group2_pmean, group3_pmean, group4_pmean),
  proportion_of_data = c(group1_pprop, group2_pprop, group3_pprop, group4_pprop)
)
usd_pledged_data

ggplot(usd_pledged_data, (aes(x= name,y = proportion_of_data))) + geom_point(aes(color = name))

```

In the usd_pledged, we see that the majority of the projects had between 0 and 100 USD pledged, next between 1000 to 10,000 and then 100-1000 at 22.5% and only about 14% pledged over 10,0000. Furthermore, we can see the averages for USD actually pledged must have some clustering especially in the group 0-100 because the average is 18USD, suggesting a large number of the projects got around $0 pledged.

